---
title: "Newbold_Brett_HW4"
output: html_document
---

---
#1
---
#### 1.a
#### Creates the vector (1,2,3,...,20)
```{r}
x1 <- c(1:20) 
x1
```
#### 1.b
#### Creates the vector (20,19,...,2,1)
```{r}
x2 <- c(20:1)   
x2
```
#### 1.c
#### Creates the vector (1,2,3,..,19,20,19,18,...,2,1)
```{r}
x3 <- c(1:20,19:1)
x3
```
#### 1.d
#### Creates the vector (4,6,3) and assigns it to the name tmp
```{r}
tmp <- c(4,6,3)
tmp
```
#### 1.e
#### Repeats the vector 10 times
```{r}
x4 <- rep(tmp, times = 10)  
x4
```
#### 1.f 
#### Repeats the vector until the desired length of 31 occurs
```{r}
x5 <- rep_len(tmp, 31)  
x5
```
#### 1.g
#### Creates a new vector based off the integer vector tmp, uses repetitions of each index of tmp a given amount of times
```{r}
x6 <- c(rep(tmp[1], each = 10), rep(tmp[2], each = 20), rep(tmp[3], each = 30))
x6
```
---
#2
---

#### seq() returns a vector (x) using its numeric arguments from 3 to 6 in increments of .1, then we create a vector (f) by inputting each value of the vector x into the function
```{r}
x <- seq(3, 6, by = .1)
f <- exp(x)*cos(x)
f
```
---
#3
---
#### 3.a
#### Creates a vector (x1) where each entry is found by the product 
```{r}
x1 <- (.1 ^ seq(3, 36, by=3))*(.2 ^ seq(1, 34, by=3))
x1
```
#### 3.b
#### Creates a vector (x2) using seq() and the default by=1
```{r}
x2 <- 2^seq(1,25)/seq(1,25)
x2
```
---
#4
---

#### 4.a
#### Returns the sum of all the values as i ascends from 10 to 100
```{r}
i <- c(10:100)
s <- sum(i^3 + 4*i^2)
s
```
#### 4.b
#### Returns the sum of all the values as i ascends from 1 to 25
```{r}
i <- c(1:25)
s <- sum((2^i)/i + (3^i)/(i^2))
s
```

---
#5
---

#### 5.a
#### Concatenates "label" term by term with the vector argument to create a character vector result, sep = " " (one space) is the default so I wont need to include it
```{r}
labels <- paste("label", c(1:30))
labels
```
#### 5.b
#### Concatenates "fn" term by term with the vector argument to create a character vector result, sep = "" with leave no space between fn and the integers
```{r}
fns <- paste("fn", c(1:30), sep = "")
fns
```

---
#6
---

#### Ensures simulated values are reproducible
```{r}
set.seed(50)
```
#### Chooses 250 integers from 0 to 999 with replacement
```{r}
xVec <- sample(0:999, 250, replace=T) 
yVec <- sample(0:999, 250, replace=T)
```

#### 6.a
#### Creates a vector by taking the difference of each component of y and x, making sure y components are "one step ahead" 
```{r}
i <- c(1:249)
a <- yVec[i+1] - xVec[i]
a
```
#### 6.b
#### Same process as part a. cos()  will be one ahead the whole time until it reaches the last entry of xVec
```{r}
i <- c(1:249)
b <- sin(yVec[i])/cos(xVec[i+1])
b
```
#### 6.c
#### Needed to shrink the i's to account for i+2 ending at 250
```{r}
i <- c(1:248)
c <- xVec[i] + 2*xVec[i+1] - xVec[i+2]
c
```
#### 6.d 
#### e's exponents will range from x2 to xn while xi will range from 1 to n-1
```{r}
i <- c(1:249)
s <- sum(exp(-xVec[i+1])/(xVec[i]+10))
s
```
---
#7
---
#### 7.a
#### Finds the index positions of yVec that are greater than 600 and yVec[] takes each of these index positions and outputs the corresponding value for each
```{r}
a <- yVec[yVec > 600]
a
```
#### 7.b
#### which() gives the indices that have a result of TRUE
```{r}
b <- which(yVec > 600)
b
```
#### 7.c
#### Finds the index positions of yVec that are greater than 600 and xVec[] takes each of these index positions and outputs the corresponding value for each
```{r}
c <- xVec[yVec > 600]
c
```

#### 7.d
#### Takes the square root of the absolute value of each difference of the components of xVec and the mean of xVec. xVec by itself just outputs x1, x2, .., xn
```{r}
d <- sqrt(abs(xVec-mean(xVec)))
d
```
#### 7.e 
#### The inequality inside finds the values of yVec that are within 200 of the maximum value including the max itself. sum() will add 1 for each TRUE output of the inequality and 0 for each FALSE.
```{r}
e <- sum(yVec > max(yVec) - 200)
e
```
#### 7.f
#### Each component of xVec will be evaluated with mod2. It will return true if the remainder is 0 (divisible by 2). sum() will add 1 for each TRUE output of the inequality and 0 for each FALSE.
```{r}
f <- sum(xVec%%2==0)
f
```
#### 7.g
#### order() returns a permutation of natural numbers that correspond to the order the original indices need to be in for it to ascend. xVec[] will be sorted in accordance with this order
```{r}
g <- xVec[order(yVec)]
g
```
#### 7.h
#### Collects the elements in yVec at index positions 1,4,7,10,.. by returning true at every 1+3n where n is a natural number
```{r}
i <- c(T,F,F)
h <- yVec[i]
h
```

---
#8
---
#### cumprod() returns the cumulative product of the elements in argument
```{r}
1 + sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2)))
```